Ms. No. PSRM-OA-2019-0126 entitled ``Taking Dyads Seriously''

### 2020-06-04 revisionMemo/rev1.tex
sync up sim code

		We have clarified our language in the paper (on page 1) to address this question.  Strategies like those employed by Aronow et al. do not directly model all relevant dependencies in the data but instead adjust the variance estimator.\footnote{As Aronow et al. explain, “Of course, accounting for dynamic dyadic clustering may fail to fully account for all relevant dependencies in the data." p. 16.}   While such an approach decreases the risk of a type 1 error, it increases risk of type 2 error (if the mean estimate is biased downwards, increasing the variance estimate will lead us to falsely accept the null). The main aim of our research is to directly account for the relevant dependency structures in the data, thus providing an accurate estimate and addressing both types of possible errors.

@@

	\item \textcolor{blue}{ \emph{ Additionally, we have SM: needs to add more here to indicate how the existing simulation section is meant to deal with this issue ... onus is on SM to bring in the problems that we highlight in the simulation section to section 2, so readers are clearer on the problem that we are trying to address

@@

>>>>

		We thank the reviewer for taking the time to provide these valuable comments. We have clarified our language in the paper (on page 1) to address this question.  Strategies like those employed by Aronow et al. do not directly model all relevant dependencies in the data but instead adjust the variance estimator. As Aronow et al. explain, "Of course, accounting for dynamic dyadic clustering may fail to fully account for all relevant dependencies in the data" (p. 16).   While such an approach decreases the risk of a type 1 error, it increases risk of type 2 error (if the mean estimate is biased downwards, increasing the variance estimate will lead us to falsely accept the null). The main aim of our research is to directly account for the relevant dependency structures in the data, thus providing an accurate estimate and addressing both types of possible errors.

@@

		\item \textcolor{blue}{ \emph{ Additionally, we have added language motivating whatn is to come in the simulation section.

@@

		We thank the reviewer for providing this reference and have added discussion of this alternative to the manuscript.
